\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % Clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Abhishek Kumar} & Email: \href{mailto:abhishek.code.jobs@gmail.com}{abhishek.code.jobs@gmail.com}\\
  \href{https://portfolio.abhishekcode.in/}{portfolio.abhishekcode.in} & Mobile: \href{tel:+918797111643}{+91 8797111643} \\
  & \href{https://github.com/abhiphile}{GitHub} $|$ \href{https://www.linkedin.com/in/abhishek-kumar-nitdelhi/}{LinkedIn} $|$ \href{https://leetcode.com/u/abhishek_nitdelhi/}{LeetCode}
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {National Institute of Technology Delhi}{New Delhi, India}
      {B.Tech in Electronics and Communication Engineering; CGPA: 7.85/10.0}{2021 -- 2025}
    \resumeSubheading
      {National Institute of Technology Delhi}{New Delhi, India}
      {Minor in AI/ML; CGPA: 8.22/10.0}{2021 -- 2025}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Oracle}{Bengaluru, India}
      {Software Development Engineer 1}{July 2025 -- Present}
      \resumeItemListStart
        \resumeItem{SBC Sizing Tool}
          {Engineered an extrapolation system using FastAPI and Oracle SQL to predict hardware requirements (CPU, cores, memory) for deployments, improving prediction accuracy by 30\%.}
        \resumeItem{MCP Automation}
          {Designed internal tools to streamline testing workflows, perform root cause analysis, and parse logs automatically, reducing debugging time by 40\%.}
        \resumeItem{Performance Optimization}
          {Collaborated with a team of 10 to enhance Session Border Controller (SBC) performance by optimizing compute utilization and reducing response latency under high-load conditions by 3\%.}
      \resumeItemListEnd

    \resumeSubheading
      {Oracle}{Bengaluru, India}
      {Software Development Intern}{Jan 2025 -- July 2025}
      \resumeItemListStart
        \resumeItem{Cloud-based SBC Tool}
          {Developed a FastAPI backend with Oracle SQL database to predict resource requirements by extrapolating datapoints; deployed on Oracle Cloud.}
        \resumeItem{Code Security}
          {Improved code security by eliminating 1,000+ instances of unsafe C/C++ functions, reducing buffer overflow and memory corruption risks.}
      \resumeItemListEnd

    \resumeSubheading
      {Google Summer of Code (SymPy)}{Remote}
      {Open Source Contributor}{May 2024 -- Sept 2024}
      \resumeItemListStart
        \resumeItem{Control Module Enhancement}
          {Contributed to SymPy's Control Module, enhancing State Space and Transfer Function classes with symbolic plotting and system interconnections (Series, Parallel, Feedback).}
        \resumeItem{Code Contributions}
          {Merged 11+ PRs with 3,000+ lines of code, 100+ unit tests, and comprehensive documentation, improving reliability for the open-source control systems community.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{CacheIt}
      {High-performance in-memory caching server in C++ with epoll and multithreading, supporting core data types (HashMap, Set, Sorted Set) and LRU/LFU eviction policies. Achieved 0.21ms avg latency and 99.99\% success rate under load. \href{https://github.com/abhiphile/cacheit}{GitHub} $\cdot$ \href{https://hub.docker.com/r/abhishek194/cacheit}{Docker Hub}}
    \resumeSubItem{Fermat MCP}
      {FastMCP server for advanced mathematical computations with NumPy, SymPy, and Matplotlib integration, enabling 50+ operations across calculus, algebra, and statistics. \href{https://github.com/abhiphile/fermat-mcp}{GitHub} $\cdot$ \href{https://smithery.ai/server/@abhishek/fermat-mcp}{Smithery MCP}}
  \resumeSubHeadingListEnd

%-----------SKILLS-----------------
\section{Technical Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{Languages}{: C++, Python, JavaScript/TypeScript, Bash}
      \hfill
      \textbf{Technologies}{: Docker, Git, GitHub Actions, Redis, Linux, CI/CD}
    }
    \item{
      \textbf{Frameworks}{: FastAPI, Express, Next.js, Crow-CPP}
      \hfill
      \textbf{Databases}{: PostgreSQL, MongoDB, MySQL, Oracle SQL}
    }
    \item{
      \textbf{Libraries}{: React, NumPy, SymPy, Matplotlib}
      \hfill
      \textbf{Concepts}{: Concurrency, Memory Management, DBMS, Design Patterns}
    }
  \resumeSubHeadingListEnd

%-----------ACHIEVEMENTS-----------------
\section{Achievements}
  \resumeSubHeadingListStart
    \item{Selected for \textbf{Google Summer of Code (GSoC) 2024}, out of 43,984 applicants from 172 countries (top 0.02\%). Contributed 3,000+ lines of code and merged 127 commits to SymPy.}
    \item{Open source contributor at \textbf{GNOME Foundation}, actively contributing to GNOME/Graphs.}
    \item{Solved 600+ LeetCode problems with a 1600+ rating, demonstrating strong problem-solving and algorithmic efficiency.}
    \item{Secured rank 32 in the competitive CodeRush coding competition.}
  \resumeSubHeadingListEnd

\end{document}
